---
title: "Hw9 – Problem 2"
output:
  html_document: default
  pdf_document:
    latex_engine: xelatex
    number_sections: true
    keep_tex: true
    toc: false
header-includes:
  - \usepackage{hyperref}
  - \hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo      = TRUE,
  warning   = FALSE,
  message   = FALSE,
  fig.width = 7,
  fig.height= 5
)
library(tidyverse)
library(broom)


```

##Problem 2: Grocery store prices

```{r cars}
# Read and clean
groceries <- read.csv("groceries.csv") %>%
  mutate(
    Store = str_trim(Store),
    Type  = str_trim(Type)
  )

```

## Part A. Average price by store

```{r pressure, echo=FALSE}
# Compute per‑store averages
store_avg <- groceries %>%
  group_by(Store) %>%
  summarize(avg_price = mean(Price, na.rm = TRUE)) %>%
  arrange(avg_price)

# Bar chart
ggplot(store_avg,
       aes(x = avg_price, y = reorder(Store, avg_price))) +
  geom_col(fill = "#4682B4") +
  labs(
    x       = "Average price (USD)",
    y       = "Store",
    caption = "Figure A: Each store’s average price across all products it stocks."
  ) +
  theme_minimal()

```

Part B. Number of stores selling each product

```{r}
# Count distinct Store×Product pairs
prod_counts <- groceries %>%
  distinct(Store, Product) %>%
  count(Product, name = "n_stores") %>%
  arrange(n_stores)

# Bar chart
ggplot(prod_counts, aes(x = n_stores, y = reorder(Product, n_stores))) +
  geom_col(fill = "#FF8C00") +
  labs(
    x       = "Number of stores carrying product",
    y       = "Product",
    caption = "Figure B: Counts top out at 16 (e.g. eggs, milk are in every store)."
  ) +
  theme_minimal()

```

Part C. Regression: Price \~ Product + Type

```{r}
# Ensure Grocery is the baseline for Type
groceries <- groceries %>%
  mutate(Type = factor(Type,
                       levels = c("Grocery",
                                  "Convenience",
                                  "High-end Grocery",
                                  "Natural",
                                  "Small Format")))

mod_type <- lm(Price ~ Product + Type, data = groceries)

# Extract 95% CI for Convenience vs Grocery
ci_conv <- confint(mod_type)["TypeConvenience", ]

sprintf(
  "Compared with ordinary grocery stores,\nconvenience stores charge between $%.2f and $%.2f more for the same product.",
  ci_conv[1], ci_conv[2]
)

```

Part D. Regression: Price \~ Product + Store

```{r}
mod_store <- lm(Price ~ Product + Store, data = groceries)

store_coefs <- broom::tidy(mod_store) %>%
  filter(str_detect(term, "^Store")) %>%
  mutate(
    store    = str_remove(term, "^Store"),
    estimate = round(estimate, 3)
  ) %>%
  arrange(estimate)

# Two lowest and two highest
low2  <- store_coefs %>% slice_head(n = 2)
high2 <- store_coefs %>% slice_tail(n = 2)

knitr::kable(
  bind_rows(low2, high2) %>% select(store, estimate),
  col.names = c("Store", "Coef (USD above baseline)"),
  caption  = "Table D: Two lowest‑ and two highest‑priced stores, controlling for product."
)

```

Part E. Central Market vs HEB

```{r}
# Pull out Central Market & HEB
cm_val  <- store_coefs %>% filter(store == "Central Market") %>% pull(estimate)
heb_val <- store_coefs %>% filter(store == "H-E-B")           %>% pull(estimate)
diff_cm_heb <- round(cm_val - heb_val, 2)
span_all     <- round(max(store_coefs$estimate) - min(store_coefs$estimate), 2)

sprintf(
  "Central Market’s coefficient = $%.2f; H‑E‑B’s = $%.2f; difference = $%.2f.  Across all stores the span is $%.2f.",
  cm_val, heb_val, diff_cm_heb, span_all
)



```

Interpretation: Central Market charges about 0.07 more than H‑E‑B for the same products, out of a total inter‑store span of 1.36.

Part F. Income effects

```{r}
groceries <- groceries %>%
  mutate(Income10K = Income / 10000)

mod_inc <- lm(Price ~ Product + Income10K, data = groceries)

beta_inc  <- coef(mod_inc)["Income10K"]
sd_inc    <- sd(groceries$Income10K)
sd_price  <- sd(groceries$Price)
std_effect<- beta_inc * sd_inc / sd_price

direction <- if (beta_inc > 0) "more" else "less"

cat(
  sprintf("1) Because Income10K’s coefficient is %.4f, higher‑income ZIP codes pay %s for the same product (per $10 000).\n",
          beta_inc, direction),
  sprintf("2) A 1‑SD increase in Income10K corresponds to a %.2f‑SD change in price.\n",
          std_effect)
)



```

Answer (F1): Lower‑income areas face higher prices, since the Income10K coefficient is negative. Answer (F2): A one‑SD rise in ZIP‑code income is associated with a -3% SD decrease in price.
